### 2009-11-29 doc/manuals/janitor/tex_future/future.tex
Merged future.tex.

\section{Representation of dynamic RTEs in the information model}
Dynamic RTEs require an extended representation in the
information model.  The Application Software description should be able
to distinguish installed RTEs from installable RTEs, potentially offer
description of extended RTE state-like information. This work is planned
to be carried out as part of the Glue-2.0 effort of OGF\footnote{OGF
GLUE: https://forge.gridforum.org/sf/projects/glue-wg}.

@@

>>>>

\section{Representation of dynamic RTEs in the information model}
Dynamic RTEs require an extended representation in the
information model.  The Application Software description should be able
to distinguish installed RTEs from installable RTEs, potentially offer
insights on the state that an dRTE is in. This work is planned
to be carried out as part of the Glue-2.0 effort of OGF\footnote{OGF
GLUE: https://forge.gridforum.org/sf/projects/glue-wg}.

@@

\section{Use of RDF}

The RDF is "correctly" used within the Janitor via the Redland libraries.
What is still missing is a semantical reasoning on what packages to
allow or disallow. For instance: allow all packages associated with
bioinformatics. This shall wait a bit longer until more experiences
on the community's demand for this service have been made.

\section{Manual Verification}

There is yet no explicit notion of a concept on how users can report
on the reliability of individual compute nodes and use such information
for the decision making on where to sent their jobs. And with an increasing
complexity of software installed, being used across versions, one will
rather trust one's very own experiences for individual sites than some
external repository or other pieces of information that may be weeks
or months old.

Consequently, no means for a manual verification and the communication
of results of such have yet been implemented.
